More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-03-27 2016-Weak-FH-Bisim/WeakBisim.tex
changes in notations (unfinished)
alphas and betas

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{def:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{	\{b_j\}^{j\in J}, \Pred, \Post}
	{s \OTarrow {v}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $b_j$
        is a transition of the hole $j$, for any action $b_j$ in the
        sort $\Sort_j$. $v$ is a variable denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $\{x_k\gets e_k\}^{k\in K}$ 
	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
	variables of the open transition.
\end{definition}

@@

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\[\Pred_{\symb{sv}}(SV, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow \bigg(
\begin{array}{l}
\exists {(a'_i)}^{i\in I},
{(b'_j)}^{j\in J},v'.\, SV=\SV{{(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}} {v'} {e_b}
\\~~\land
\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land e_b
\end{array} \bigg)\]

@@

	\noindent
\begin{mathpar}
    \mprset {vskip=1ex}
\inferrule
    {
\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} \\
\\     	
	\forall m\!\!\in\!\! I_1. {\pNet_m 
	\models\mprset{myfraction=\reddottedrule}\inferrule
    	{
    	\{{b_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\mprset{myfraction=\reddottedrule}\inferrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} }\\\\
     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in (I_1\uplus I_2)},b_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
    }
    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\mprset{myfraction=\reddottedrule}\inferrule
    		{
    		\{{b_j}\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
\end{mathpar}    
	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {
           \{{b_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {v} s'}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
    \inferrule*[myfraction=\reddottedrule]
         {
           \{{b_{j x}}\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTarrow {v_x} t_x}
%         \right)
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.

@@

 \begin{mathpar}
 \inferrule*[myfraction=\reddottedrule]
         {
           \{{b_j}\}^{j\in J_1},\Pred,\Post}
         {s \OTWeakarrow {v} s'}
         \in \mathcal{T}^*
 \end{mathpar}

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {
           \{{b_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {v} s'}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2^*$:
 \begin{mathpar}
    \inferrule*[myfraction=\reddottedrule]
         {
           \{{b_{j x}}\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {v_x} t_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

@@

       	\inferrule*[myfraction=\reddottedrule]
       	{
       		\{{b_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
       	{s \OTarrow {v} {s}'}

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{
       		\{{b_{j p x}}\}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
       	{t_p \OTarrow {v_{px}} t_{p x}}
       	%         \right)
       	\end{mathpar}

@@

       	$\Pred_{s,p} \land \Pred_{OT}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       	\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
       	\land v\!=\!v_{px} \land
       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$\\

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{
       		\{{b_{j p x y}}\}^{j\in J_{pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTarrow {v_{pxy}} u_{pxy}}
       	%         \right)

       	\end{mathpar}
       	such that  $\forall y, J_{px}=J_{pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. b_{jpx}=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land v_{px}\!=\!v_{pxy} \land
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$\\.

@@

       	Second, by definition of bisimulation we need (recall that $\Pred_{s,u}$ is the 
       	original predicate relating $s$ and $u$ by definition of the transitive 
       	closure):\\
       	\begin{small}
       		$\Pred_{s,u} \land \Pred_{OT}\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
       		\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       		\land v\!=\!v_{pxy} \land
       		\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
       	\end{small}
\TODO{From we will add notation (1) and (2)}        	
       	We have, for all $p$
       	\begin{small}
       		$\Pred_{s,p} \land \Pred_{OT}\land\Pred_{p,u}\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred_{p,u}\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\left( \forall j. b_j=b_{jpx}  \Rightarrow (\Pred_{OT_{px}}\land\Pred_{p,u})
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\big( \forall j. b_j=b_{jpx}  \Rightarrow (\bigvee_{y\in Y} 
       		\big( \forall j'. b_{j'px}=b_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
       		\land v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\big))
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
       		\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
       		\Rightarrow \big( 
       		\Pred_{OT_{pxy}}
       		\land v\!=v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
       		\land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\big)
       		$

@@

      	\begin{small}     	
$\Pred_{s,u} \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{p\in P} (
	\Pred_{s,p}\land\Pred_{p,u} \land \Pred_{OT})\\
\hspace{1cm} \implies\!\!\!\bigvee_{p\in P}
 \bigvee_{x\in X} \bigvee_{y\in Y}
\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
\Rightarrow \big( 
\Pred_{OT_{pxy}}
\land v\!=v_{px}\!=\!v_{pxy}\\~\hspace{3em}~ \land
\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\big)\big)
\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
\land v\!=\!v_{pxy} \land
\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
  \end{small}

@@

\begin{lemma}[OT decomposition]\label{lem-decompose} 
	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\mprset{myfraction=\reddottedrule}\inferrule
			{
				\{{b_j}\}^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTarrow {v}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $I\cap L_Q\neq 
		\emptyset$, i.e. $Q$ takes part in the reduction.
		 Then there exist $v_Q$, $\Pred\,'$, $\Pred\,''$, 
		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\mprset{myfraction=\reddottedrule}\inferrule
			{
				\{{b_j}\}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {v}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and~~}
		%\[
		Q\models{\mprset{myfraction=\reddottedrule}\inferrule
			{
				\{\xrightarrow{b_j}\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
				\Post\,''}
			{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
				\ostate{s_i'^{\,i\in L_Q}}}
		}%\]
		\end{mathpar}
		and  $\Pred\subst{v_Q\leftarrow b_{j_0}} =(\Pred\,'
		\land \Pred\,'')$, $\Post=\Post\,'\uplus 
		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
		$\Leaves(Q)$.
\end{lemma}

>>>>

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{def:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{	\{\beta_j\}^{j\in J}, \Pred, \Post}
	{s \OTarrow {v}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $b_j$
        is a transition of the hole $j$, for any action $b_j$ in the
        sort $\Sort_j$. $v$ is a variable denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states $s_i$, $\beta_j$, $s$, $v$. \Post\ is a set of equations 
	that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $\{x_k\gets e_k\}^{k\in K}$ 
	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
	variables of the open transition.
\end{definition}

@@

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\[\Pred_{\symb{sv}}(SV, \alpha_i^{i\in I}, \beta_j^{j\in J}, v)\Leftrightarrow \bigg(
\begin{array}{l}
\exists {(\alpha'_i)}^{i\in I},
{(\beta'_j)}^{j\in J},v'.\, SV=\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} {v'} 
{e_b}
\\~~\land
\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land v=v' 
\land e_b
\end{array} \bigg)\]

@@

	\noindent
\begin{mathpar}
    \mprset {vskip=1ex}
\inferrule
    {
\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} \\
\\     	
	\forall m\!\!\in\!\! I_1. {\pNet_m 
	\models\mprset{myfraction=\reddottedrule}\inferrule
    	{
    	\{{\beta_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\mprset{myfraction=\reddottedrule}\inferrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} }\\\\
     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',\beta_j,v) 
    }
    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\mprset{myfraction=\reddottedrule}\inferrule
    		{
    		\{{\beta_j}\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
\end{mathpar}    
	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {
           \{{\beta_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {v} s'}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \overline{\alpha_i}, \overline{b_j}, v_x.\ \
    \inferrule*[myfraction=\reddottedrule]
         {
           \{{\beta_{j x}}\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTarrow {v_x} t_x}
%         \right)
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. \beta_j=\beta_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.

@@

 \begin{mathpar}
 \inferrule*[myfraction=\reddottedrule]
         {
           \{{\beta_j}\}^{j\in J_1},\Pred,\Post}
         {s \OTWeakarrow {v} s'}
         \in \mathcal{T}^*
 \end{mathpar}

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {
           \{{\beta_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {v} s'}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2^*$:
 \begin{mathpar}
    \inferrule*[myfraction=\reddottedrule]
         {
           \{{\beta_{j x}}\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {v_x} t_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. \beta_j=\beta_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

@@

       	\inferrule*[myfraction=\reddottedrule]
       	{
       		\{{\beta_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
       	{s \OTarrow {v} {s}'}

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{
       		\{{\beta_{j p x}}\}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
       	{t_p \OTarrow {v_{px}} t_{p x}}
       	%         \right)
       	\end{mathpar}

@@

       	$\Pred_{s,p} \land \Pred_{OT}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       	\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow \Pred_{OT_{px}}
       	\land v\!=\!v_{px} \land
       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$\\

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{
       		\{{\beta_{j p x y}}\}^{j\in J_{pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTarrow {v_{pxy}} u_{pxy}}
       	%         \right)

       	\end{mathpar}
       	such that  $\forall y, J_{px}=J_{pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. \beta_{jpx}=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land v_{px}\!=\!v_{pxy} \land
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$\\.

@@

       	Second, by definition of bisimulation we need (recall that $\Pred_{s,u}$ is the 
       	original predicate relating $s$ and $u$ by definition of the transitive 
       	closure):\\
       	\begin{small}
       		$\Pred_{s,u} \land \Pred_{OT}\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
       		\left( \forall j. \beta_j=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       		\land v\!=\!v_{pxy} \land
       		\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
       	\end{small}
\TODO{From we will add notation (1) and (2)}        	
       	We have, for all $p$
       	\begin{small}
       		$\Pred_{s,p} \land \Pred_{OT}\land\Pred_{p,u}\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow \Pred_{OT_{px}}
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred_{p,u}\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow 
       		(\Pred_{OT_{px}}\land\Pred_{p,u})
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\big( \forall j. \beta_j=\beta_{jpx}  \Rightarrow (\bigvee_{y\in Y} 
       		\big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
       		\land v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\big))
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
       		\big( \forall j, j'. \beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
       		\Rightarrow \big( 
       		\Pred_{OT_{pxy}}
       		\land v\!=v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
       		\land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\big)
       		$

@@

      	\begin{small}     	
$\Pred_{s,u} \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{p\in P} (
	\Pred_{s,p}\land\Pred_{p,u} \land \Pred_{OT})\\
\hspace{1cm} \implies\!\!\!\bigvee_{p\in P}
 \bigvee_{x\in X} \bigvee_{y\in Y}
\big( \forall j, j'. \beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
\Rightarrow \big( 
\Pred_{OT_{pxy}}
\land v\!=v_{px}\!=\!v_{pxy}\\~\hspace{3em}~ \land
\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\big)\big)
\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
\left( \forall j. \beta_j=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
\land v\!=\!v_{pxy} \land
\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
  \end{small}

@@

\begin{lemma}[OT decomposition]\label{lem-decompose} 
	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\mprset{myfraction=\reddottedrule}\inferrule
			{
				\{{\beta_j}\}^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTarrow {v}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $I\cap L_Q\neq 
		\emptyset$, i.e. $Q$ takes part in the reduction.
		 Then there exist $v_Q$, $\Pred\,'$, $\Pred\,''$, 
		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\mprset{myfraction=\reddottedrule}\inferrule
			{
				\{{\beta_j}\}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {v}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and~~}
		%\[
		Q\models{\mprset{myfraction=\reddottedrule}\inferrule
			{
				\{\xrightarrow{\beta_j}\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
				\Post\,''}
			{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
				\ostate{s_i'^{\,i\in L_Q}}}
		}%\]
		\end{mathpar}
		and  $\Pred\subst{v_Q\leftarrow \beta_{j_0}} =(\Pred\,'
		\land \Pred\,'')$, $\Post=\Post\,'\uplus 
		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
		$\Leaves(Q)$.
\end{lemma}

   \begin{small}\begin{proof}
Consider rule TR2 in 
       Definition~\ref{def:operationalSemantics}. 
	\begin{description}
		\item[{\bf Tr2:}]
	\end{description}
	\noindent
    $\inferrule
    {
	\forall m\!\!\in\!\! I_1. {\pNet_m \models\mprset{myfraction=\reddottedrule}\inferrule
    	{
    	\{{\beta_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\mprset{myfraction=\reddottedrule}\inferrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} }\\\\
\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} \\
\\     	
     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',\beta_j,v) 
    }
    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{
    		\{{\beta_j}\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $
	\medskip
